Trends from 30-Year Observations of Downward Solar Irradiance in Thessaloniki, Greece

### 2024-01-02 MDPI_submission.Rmd
Commit 2024-01-02 21:12

\vspace{+100pt}

@@

@@

We have analyzed a 30-year dataset of SRD measurements in Thessaloniki Greece 
(`r paste(year(min(ALL_1_daily_DESEAS$Date)), " -- ", year(max(ALL_1_daily_DESEAS$Date)))`), aiming to identify the long-term variability of
solar irradiance under different sky conditions.
Under all-sky conditions 
there is a positive trend in SDR of $`r alltrend`\,\%/y$ (brightening). 
A previous study [@Bais2013] for the period 1993 -- 2011 reported also a positive trend of $0.33\,\%/y$.
The slight increase of this trend indicates that the brightening of SDR continues and is likely caused by continuing decreases in aerosol optical depth and the optical thickness of clouds over the area.
A smaller trend has
been found under clear-sky conditions ($`r cleartrend`\,\%/y$) which supports the
notion that part of the brightening is caused by decreasing aerosols.
@Siomos2020 have shown that aerosol optical depth over
Thessaloniki is decreasing constantly at least up to 2018.
The attenuation
of SDR by aerosols over Europe has been proposed as major factor by @Wild2021.
Unfortunately, for this study aerosol data for the entire period were
not available in order to quantify their effect on SDR. 
The brightening effect on SDR under cloudy-sky conditions
($`r cloudtrend`\,\%/y$), suggests that cloud optical thickness is also decreasing
during this period.
As long term data of cloud optical thickness are
also not available for the region, we cannot draw quantitative
conclusions.
<!-- @Lozano2023 reported a Cloud Radiative Forcing (CRF) SDR trend of $1.22\,W/m^2/y$ for the city of Granada Spain ($37^\circ\,10'\,$N, $3^\circ\,37'\,$E, $680\,$m\ a.s.l.).  -->
 <!-- (37.16◦ N, 3.61◦ W, 680 m a.s.l.), 37° 9' 35.9994" N  3° 36' 35.9994" W    ($37^\circ\,10'\,$N, $3^\circ\,37'\,$E, $680\,$m\ a.s.l.)-->
<!-- We found a comparable result, for the same parameter, using the long term trend of all- and clear-skies, as follows $\text{CRF} = 1.46 - 0.501 = `r 1.46 - 0.501`\,W/m^2/y$. -->

>>>>

@@

\ \

\ \

\ \

\ \

\ \

\ \

\ \

\ \

\ \

\ \

\ \

\ \

\ \

\ \

\ \

\ \

\ \

@@

We have analyzed a 30-year dataset of SRD measurements in Thessaloniki, Greece 
(`r paste(year(min(ALL_1_daily_DESEAS$Date)), " -- ", year(max(ALL_1_daily_DESEAS$Date)))`), aiming to identify the long-term 
variability of solar irradiance under different sky conditions.
Under all-sky conditions, there is a positive trend in SDR of 
$`r alltrend`\,\%/y$ (brightening). 
A previous study [@Bais2013] for the period 1993--2011 also reported a
positive trend of $0.33\,\%/y$.
The slight increase in this trend indicates that the brightening of SDR
continues and is likely caused by continuing decreases in aerosol optical
depth and the optical thickness of clouds over the area.
A smaller trend has been found under clear-sky conditions
($`r cleartrend`\,\%/y$), which supports the notion that part of the
brightening is caused by decreasing aerosols.
@Siomos2020 showed that aerosol optical depth over Thessaloniki
was decreasing constantly, at least up until 2018.
The attenuation of SDR by aerosols over Europe has been proposed as
major factor by @Wild2021.
Unfortunately, for this study, aerosol data for the entire period were
not available in order to quantify their effect on SDR. 
The brightening effect on SDR under cloudy-sky conditions
($`r cloudtrend`\,\%/y$) suggests that cloud optical thickness 
is also decreasing during this period.
As long-term data of cloud optical thickness are
also not available for the region, we cannot draw quantitative
conclusions.
<!-- @Lozano2023 reported a Cloud Radiative Forcing (CRF) SDR trend of $1.22\,W/m^2/y$ for the city of Granada Spain ($37^\circ\,10'\,$N, $3^\circ\,37'\,$E, $680\,$m\ a.s.l.).  -->
 <!-- (37.16◦ N, 3.61◦ W, 680 m a.s.l.), 37° 9' 35.9994" N  3° 36' 35.9994" W    ($37^\circ\,10'\,$N, $3^\circ\,37'\,$E, $680\,$m\ a.s.l.)-->
<!-- We found a comparable result, for the same parameter, using the long term trend of all- and clear-skies, as follows $\text{CRF} = 1.46 - 0.501 = `r 1.46 - 0.501`\,W/m^2/y$. -->

### 2024-01-02 MDPI_submission.tex
Commit 2024-01-02 21:12

@@

We have analyzed a 30-year dataset of SRD measurements in Thessaloniki
Greece (1993 -- 2023), aiming to identify the long-term variability of
solar irradiance under different sky conditions. Under all-sky
conditions there is a positive trend in SDR of \(0.38\,\%/y\)
(brightening). A previous study \citep{Bais2013} for the period 1993 --
2011 reported also a positive trend of \(0.33\,\%/y\). The slight
increase of this trend indicates that the brightening of SDR continues
and is likely caused by continuing decreases in aerosol optical depth
and the optical thickness of clouds over the area. A smaller trend has
been found under clear-sky conditions (\(0.097\,\%/y\)) which supports
the notion that part of the brightening is caused by decreasing
aerosols. \citet{Siomos2020} have shown that aerosol optical depth over
Thessaloniki is decreasing constantly at least up to 2018. The
attenuation of SDR by aerosols over Europe has been proposed as major
factor by \citet{Wild2021}. Unfortunately, for this study aerosol data
for the entire period were not available in order to quantify their
effect on SDR. The brightening effect on SDR under cloudy-sky conditions
(\(0.41\,\%/y\)), suggests that cloud optical thickness is also
decreasing during this period. As long term data of cloud optical
thickness are also not available for the region, we cannot draw
quantitative conclusions.

>>>>

~~

~~

~~

~~

~~

~~

~~

~~

~~

~~

~~

~~

~~

~~

~~

~~

~~

@@

We have analyzed a 30-year dataset of SRD measurements in Thessaloniki,
Greece (1993 -- 2023), aiming to identify the long-term variability of
solar irradiance under different sky conditions. Under all-sky
conditions, there is a positive trend in SDR of \(0.38\,\%/y\)
(brightening). A previous study \citep{Bais2013} for the period
1993--2011 also reported a positive trend of \(0.33\,\%/y\). The slight
increase in this trend indicates that the brightening of SDR continues
and is likely caused by continuing decreases in aerosol optical depth
and the optical thickness of clouds over the area. A smaller trend has
been found under clear-sky conditions (\(0.097\,\%/y\)), which supports
the notion that part of the brightening is caused by decreasing
aerosols. \citet{Siomos2020} showed that aerosol optical depth over
Thessaloniki was decreasing constantly, at least up until 2018. The
attenuation of SDR by aerosols over Europe has been proposed as major
factor by \citet{Wild2021}. Unfortunately, for this study, aerosol data
for the entire period were not available in order to quantify their
effect on SDR. The brightening effect on SDR under cloudy-sky conditions
(\(0.41\,\%/y\)) suggests that cloud optical thickness is also
decreasing during this period. As long-term data of cloud optical
thickness are also not available for the region, we cannot draw
quantitative conclusions.
